cardinalR: Generating interesting high-dimensional data structures

### 2025-10-22 paper-cardinalR.Rmd
Added langevitour to the center

branchfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    orglinearbranches_lang
  ),
  device = "xs"
)

@@

conefig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    cone_lang
  ),
  device = "xs"
)

@@

pyrfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    pyrrect_lang, pyrtri_lang, pyrstar_lang, pyrholes_lang
  ),
  device = "xs"
)

@@

spherefig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    circle_lang, curvycycle_lang, clusteredspheres_lang
  ),
  device = "xs"
)

@@

trefoilfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    trefoil4d_lang, trefoil3d_lang
  ),
  device = "xs"
)

@@

triginometricfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    curvycylinder_lang, sphericalspiral_lang, conicspiral_lang, nonlinear_lang
  ),
  device = "xs"
)

>>>>

branchfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;",
    orglinearbranches_lang
  ),
  device = "xs"
)

@@

conefig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;",
    cone_lang
  ),
  device = "xs"
)

@@

pyrfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;",
    pyrrect_lang, pyrtri_lang, pyrstar_lang, pyrholes_lang
  ),
  device = "xs"
)

@@

spherefig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;",
    circle_lang, curvycycle_lang, clusteredspheres_lang
  ),
  device = "xs"
)

@@

trefoilfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;",
    trefoil4d_lang, trefoil3d_lang
  ),
  device = "xs"
)

@@

triginometricfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;",
    curvycylinder_lang, sphericalspiral_lang, conicspiral_lang, nonlinear_lang
  ),
  device = "xs"
)
